\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Font options
\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Gouranga Das Samrat} \\ \vspace{1pt}
    \small Full-Stack Developer \\ \vspace{1pt}
    \small +880 1873 966 298 $|$ \href{mailto:gouranga.samrat@gmail.com}{gouranga.samrat@gmail.com} \\
    \href{https://linkedin.com/in/yourusername}{\underline{Linkedin}} $|$ 
    \href{https://yourportfolio.com}{\underline{Portfolio}} $|$ 
    \href{https://github.com/yourusername}{\underline{GitHub}}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Web Developer Intern}{September 2025 -- October 2025}
      {Labmentix}{Remote}
      \resumeItemListStart
        \resumeItem{Built a Full-Stack Google Drive Clone using modern web technologies (MERN Stack).}
        \resumeItem{Collaborated with team members to improve UI/UX design and optimize performance.}
        \resumeItem{Gained hands-on experience in full-stack development workflow and Git-based version control.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Frontend}{: JavaScript, TypeScript, React JS, Next JS, Tailwind CSS, Bootstrap} \\
     \textbf{Backend}{: Node JS, Express JS} \\
     \textbf{Databases}{: MongoDB, MySQL} \\
     \textbf{DevOps}{: Docker, CI/CD, Linux}
    }}
 \end{itemize}

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{PDF Merger} $|$ \emph{React JS, Bootstrap 5, pdf-merger-js, Clerk}}{}
          \resumeItemListStart
            \resumeItem{Developed PDF Hero, allowing users to view, edit, merge, and split PDF files.}
            \resumeItem{Implemented an intuitive and responsive interface for seamless operations across devices.}
            \resumeItem{Optimized PDF processing for speed and reliability, supporting multiple file formats.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{3D Portfolio} $|$ \emph{React JS, Tailwind CSS, Three JS, Framer Motion}}{}
          \resumeItemListStart
            \resumeItem{Developed a 3D responsive Portfolio with a 3D island, project section, and contact form.}
            \resumeItem{Ensured engaging user experience through intuitive design and smooth animations.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Weather App} $|$ \emph{React JS, Tailwind CSS, OpenWeatherMap API, Recharts}}{}
          \resumeItemListStart
            \resumeItem{Integrated real-time weather data with dynamic UI and location-based search.}
            \resumeItem{Built a TypeScript-powered architecture to ensure performance, scalability, and type safety.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{Certifications}
    \resumeSubHeadingListStart
      \resumeProjectHeading{\textbf{Software Engineer Intern} -- HackerRank}{}
      \resumeProjectHeading{\textbf{Front End Development Libraries} -- freeCodeCamp}{}
      \resumeProjectHeading{\textbf{JavaScript Algorithms and Data Structures} -- freeCodeCamp}{}
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Khulna Government Model School \& College}{September 2025 -- Present}
      {Higher Secondary Certificate (HSC)}{Khulna, Bangladesh}
  \resumeSubHeadingListEnd

\end{document}
